Title

### 2018-07-31 thesis/paper/paper.tex
Added one-of

>>>>

\subsection{One-of (Q21510859)}
The one-of constraint fits in the pattern established by the previous two constraints and disallows certain property-value combinations. With \(A\) the set of allowed values the rules for triple, qualifier and reference are respectively:
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{tripleEDB}(S, I, \text{propertyConstant}, V) \wedge \text{unequal}(\{A\}, V)
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{violation\_qualifier}&(S, \text{propertyConstant}, V) \leftarrow \\
&\text{qualifierEDB}(S, \text{propertyConstant}, V) \wedge \text{unequal}(\{A\}, V)
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{violation\_reference}&(S, \text{propertyConstant}, V) \leftarrow \\
&\text{referenceEDB}(S, \text{propertyConstant}, V) \wedge \text{unequal}(\{A\}, V)
\end{split}
\end{equation*}
